---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# details

Simple function for creating a details block for markdown documents.

## Installation

``` r
remotes::install_github("yonicd/details")
```

## Example

The function `details::details` can output to result either to `console` (default), `clipboard` (via clipr) or to the R `file.editor` pop up (useful when clipr not available).

For this document it makes most sense to use the default output (`console`).

## Character

### Basic

```{r,results='asis'}
library(magrittr)

sessioninfo::session_info()%>%
  details::details(summary = 'current session info')
```

### Open by default

```{r,results='asis'}
sessioninfo::session_info()%>%
  details::details(summary = 'open session info',open = TRUE)
```

### Custom tooltip

```{r,results='asis'}
sessioninfo::session_info()%>%
  details::details(summary = 'session info with date tooltip ', tooltip = Sys.Date())
```

### Highlight Language

```{r,results='asis'}

readLines('https://raw.githubusercontent.com/metrumresearchgroup/covrpage/master/_pkgdown.yml')%>%
  details::details(summary = 'yaml example',lang = 'yml')
```

## data.frame/tibble

### data.frame

```{r,results='asis'}
 iris%>%
  details::details(summary = 'data.frame')
```

### tibble

```{r,results='asis'}
 iris%>%
  tibble::as_tibble()%>%
  details::details(summary = 'tibble')
```

## lists

```{r,results='asis'}
 list(a = 1,b = head(iris))%>%
  details::details(summary = 'list')
```
